### 2017-03-08 Manuscripts/cog-psych/cogpsych.tex
more manuscript updates!

\documentclass[12pt]{article}
\usepackage[letterpaper, margin=1in, headheight=15pt]{geometry}
\usepackage{amsmath}
\usepackage{setspace}
\usepackage{pgfplots}
\usepackage{fancyhdr}
\usepackage{fancyvrb}
\usepackage{csquotes}
\usepackage[natbibapa]{apacite}

@@

@@

Creating Something Different: Similarity and Contrast Effects in Concept Generation.
% ---- other ideas:
% - The Role of Contrast in Concept Generation.
% - Creating Something Different: The Role of Contrast in Concept Generation.
% - Something New: The Role of Contrast in Concept Generation.
% - What's New In Concept Generation? The Role of Category Contrast.

@@

Filler!

@@

% [[NBC]] Explain copy and tweak here?

@@

% [[NBC]] explain their models here...

It is worth noting, however, that the literature reviewed above provides only a limited view of category generation: the main focus of the published experiments has been on the distributional correspondences between learned and generated categories. In this paper, we seek to identify other important constraints on the processes involved in creative generation. We also introduce a novel exemplar-based model of category generation, PACKER (\textit{Producing Alike and Contrasting Knowledge using Exemplar Representations}), which explains much of what we observe in the creative use of conceptual knowledge. In the sections below, we introduce the PACKER model and its core theoretical claims.

@@

In order to generate a novel concept, individuals must produce something that is in some capacity \textit{different} from what they already know. Thus, in a trivial sense, contrast can be viewed as a fundamental constraint on creative generation: new concepts must firstly be different from existing ones. However the role of contrast in category generation has not been systematically evaluated: how do people generate concepts such that the product is (A) different from what is already known, and (B) internally coherent?

@@

>>>>

\documentclass[12pt]{article}
\usepackage[letterpaper, margin=1in, headheight=15pt]{geometry}
\usepackage{amsmath}
\usepackage{setspace}
\usepackage{pgfplots}
\usepackage{fancyhdr}
\usepackage{fancyvrb}
\usepackage{csquotes}
\usepackage{todonotes}
\usepackage{verbatim}
\usepackage[natbibapa]{apacite}

@@

% set up notes-- different backgrounds for Nolan and Joe!
\newcommand\nbcnote[1]{\todo[inline, backgroundcolor = yellow]{\textbf{NBC}: #1}}
\newcommand\jlanote[1]{\todo[inline, backgroundcolor = lime]{\textbf{JLA}: #1}}

@@

Creating Something Different: Similarity and Contrast Effects in Concept Generation.
% ---- other ideas:
% - The Constraining Influences of Contrast and Similartity in Concept Generation.

@@

\jlanote{Joe! Did you know i made a command for you to enter in comments like this?? }

\begin{verbatim}
    \jlanote{Some note}
\end{verbatim}

@@

\nbcnote{Explain Copy + Tweak here?}

@@

\nbcnote{explain hierarchical sampling here, maybe also their implementation of copy+tweak? Or maybe we should step away from copy+tweak as a relevant option. Or maybe we focus on systematically comparing their copy and tweak to PACKER with specific params? This copy and tweak issue makes for a mess... }

@@

It is worth noting that the literature reviewed above provides a somewhat limited view of category generation: the main concern of the published experiments has been on the distributional correspondences between learned and generated categories. In this paper, we seek to identify other important constraints on the processes involved in creative generation. Specifically, we focus on the constraints imposed by category contrast. That is, in order to generate a novel concept, individuals must produce something that is in some capacity \textit{different} from what they already know. Thus, in a trivial sense, contrast can be viewed as a fundamental constraint on creative generation: new concepts must firstly be different from existing ones.

Although it is evident that people are \textit{capable} of creating new concepts and categories, it is not altogether clear how new concepts are systematically made different from what is already known. The hierarchical sampling model developed by \cite{jern2013probabilistic}, for example, does not provide any strong claims about how generated categories should contrast with learned ones: it is simply assumed that categories are generated in a random location in the domain.

The Copy+Tweak account evaluated by Ward \& colleagues \citep{ward1995s,ward2002role} makes a slightly stronger claim: new categories should be .....

%

@@

\nbcnote{Just some random snippets that i don't want to delete yet...}

How do people generate concepts such that the product is (A) different from what is already known, and (B) internally coherent?

We also introduce a novel exemplar-based model of category generation, PACKER (\textit{Producing Alike and Contrasting Knowledge using Exemplar Representations}), which explains much of what we observe in the creative use of conceptual knowledge. In the sections below, we introduce the PACKER model and its core theoretical claims.
